Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-27 manuscript/manuscript.tex
ms changes
ms updates

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/gss-zbar.pdf}

  \caption{The population mean trait value under the Gaussian stabilizing
  selection simulations (gray lines) and the trait optima (dashed blue lines).
  The first row shows the selection response during a graduate shift in optima
  per generation, while the second row shows the selection response during a
  sudden optima shift.}
